quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-20 paper-quollr-submission-v1/paper-quollr.tex
Prepare submission for R Journal

\begin{figure}[H]
\includegraphics[width=1\linewidth,alt={The figure is a schematic diagram illustrating the quollr workflow and software architecture. Rectangular boxes represent processing steps and data objects, including NLDR and p-D data inputs, data preprocessing, hexagonal binning, centroid computation, triangulation, and construction of a 2-D mesh. Arrows indicate the flow of information between steps, from the input data through the 2-D mesh, and then from the mesh being lifted into the p-D space. Additional boxes show prediction and error computation for new data, as well as interactive components that link the p-D and 2-D representations. The diagram is laid out sequentially, showing how data move through the system from input to interactive output.}]{figures/quollr_workflow} \caption{Overview of the `quollr` workflow and software architecture. The process begins with NLDR and $p\text{-}D$ data inputs, followed by data preprocessing and hexagonal binning. Centroids are computed and triangulated to form the $2\text{-}D$ mesh, which is then lifted into the $p\text{-}D$ space. Predictions and error computations are performed on new data, while interactive functions enable dynamic linking between the $p\text{-}D$ and $2\text{-}D$ representations.}\label{fig:workflow}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth,alt={The figure is a schematic diagram illustrating the quollr workflow and software architecture. Rectangular boxes represent processing steps and data objects, including NLDR and p-D data inputs, data preprocessing, hexagonal binning, centroid computation, triangulation, and construction of a 2-D mesh. Arrows indicate the flow of information between steps, from the input data through the 2-D mesh, and then from the mesh being lifted into the p-D space. Additional boxes show prediction and error computation for new data, as well as interactive components that link the p-D and 2-D representations. The diagram is laid out sequentially, showing how data move through the system from input to interactive output.}]{figures/quollr_workflow} \caption{Overview of the \texttt{quollr} workflow and software architecture. The process begins with NLDR and $p\text{-}D$ data inputs, followed by data preprocessing and hexagonal binning. Centroids are computed and triangulated to form the $2\text{-}D$ mesh, which is then lifted into the $p\text{-}D$ space. Predictions and error computations are performed on new data, while interactive functions enable dynamic linking between the $p\text{-}D$ and $2\text{-}D$ representations.}\label{fig:workflow}
\end{figure}
